%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-2.0pt}
\setlength{\columnsep}{0pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\definecolor{linkcolor}{RGB}{0,102,204}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    urlcolor=linkcolor
}

% Custom commands
\newcommand{\resumeItem}[1]{%
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Chirag Bisht} \\ \vspace{3pt}
    Noida \\ \vspace{3pt}
    \small \raisebox{-0.1\height}\faPhone\ 8800538990 ~ \href{mailto:chiragbisht2003@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{chiragbisht2003@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/chiragbisht/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/chiragbisht}}  ~
    \href{https://github.com/Chiragbisht}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/Chiragbisht}}
    \vspace{-2pt}
\end{center}

\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    Software Engineer with experience in Python, Django, and full-stack web development. Skilled in integrating APIs, implementing Agile methodologies, and deploying containerized applications with Docker.
    }}
\end{itemize}
\vspace{-10pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Inderprastha Engineering College}{11/2021 -- 6/2025}
      {Bachelor of Technology in Information Technology}{Sahibabad,UttarPradesh}
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Django, SQL, CSS, Mongodb, Typescript, React} \\
     \textbf{Developer Tools}{: Github,Docker,Digital Ocean} \\
     \textbf{Technologies}{: Prompt Engineering, Agentic coding, AI Agents, Prompt Design} \\
     \textbf{Ai Tools}{: Claude code, Cursor, Windsurf, Lovable, Figma} 
    }}
 \end{itemize}
 \vspace{-12pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Easemyexpo}{03/2025 -- Present}
      {Software Developer (remote)}{}
      \resumeItemListStart
        \resumeItem{Part of the founding tech team, contributing to architectural decisions and core development strategies.}
        \resumeItem{Worked on FastAPI backends and MongoDB for building robust APIs with comprehensive data validation.}
        \resumeItem{Developed frontend using React and Vite to build a lead generation application with modern UI/UX.}
        \resumeItem{Helped scale the product from 0 to 150 monthly active users (MAU) through performance optimization.}
      \resumeItemListEnd

    \resumeSubheading
      {CISCO Cybersecurity}{05/2024 -- 07/2024}
      {Intern (remote)}{}
      \resumeItemListStart
        \resumeItem{Developed a comprehensive network architecture for a college, connecting various department PCs and lab systems to simulate real-world administrative networks and reducing network latency by 15\%.}
        \resumeItem{Implemented firewall configurations and cybersecurity measures that reduced potential security breaches by 25\%.}
        \resumeItem{Conducted performance testing and troubleshooting to ensure the robustness of routing protocols under load.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
\vspace{-5pt}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{Lead Generation SaaS Tool} $|$ \emph{\href{https://leads.easemyexpo.in/}{Live Preview}}}{05/2025 -- 07/2025 }
      \resumeItemListStart
        \resumeItem{Lead generation SaaS tool made core functionality of SaaS tool backend FastAPI, optimised for performance and UX.}
        \resumeItem{Worked on Vite React frontend for ultra fast frontend building and MongoDB for database management.}
        \resumeItem{Implemented scalable architecture to handle multiple concurrent users and data processing.}
      \resumeItemListEnd
      \vspace{-13pt}
  \resumeProjectHeading
      {\textbf{Humanizer} $|$ \emph{\href{https://humanizer-olive.vercel.app/}{Live Preview}}}{01/2025 -- 02/2025}
      \resumeItemListStart
        \resumeItem{Developed an AI-driven application using GeminiAPI, and Groq API to detect and rephrase AI-generated content, increasing content naturalness by 80\%.}
        \resumeItem{Utilized advanced prompt engineering and Sonnet 3.7 to reduce AI hallucinations by 30\% and enhance accuracy.}
        \resumeItem{Developed an app that improved AI response accuracy by 50\% using advanced optimization techniques.}
      \resumeItemListEnd
      \vspace{-13pt}
  \resumeProjectHeading
      {\textbf{Chat Room} $|$ \emph{\href{https://chatroom-os4ddry5.b4a.run/}{Live Preview}} }{07/2024 -- 09/2024}
      \resumeItemListStart
        \resumeItem{Built a scalable chat room application using Django with fully implemented user authentication.}
        \resumeItem{Implemented real-time messaging with polling techniques, reducing message latency by 50\%.}
        \resumeItem{Created responsive front-end designs using Tailwind CSS, with HTML generated through generative AI models.}
        \resumeItem{Designed backend architecture and models to support 50+ concurrent users.}
      \resumeItemListEnd 
\resumeSubHeadingListEnd
\vspace{-15pt}

%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
\resumeSubHeadingListStart
  \resumeItemListStart
    \resumeItem{Represented university in National Esports Tournament and secured 3rd position.}
    \resumeItem{Founding member of Esports Club and conducted multiple events.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}
